### 2024-05-01 content/chapter_2.tex
:triangular_flag_on_post: Viva

		Conventional metamaterials have fixed properties that depend on the geometry and arrangement of their constituent elements.
		Once fabricated, these properties cannot be easily changed unless the structure is physically altered.
		This limits their early usage to military and defense, with applications such as invisibility cloaks and optical illusions.
		In 2014, the concept of ``coding'' and ``programmable'' metamaterials was validated by researchers at Southeast University \cite{Cui2014}, who realized digital control of radar cross-section using biased diodes and \gls{fpga}.
		With a proper model of the target properties and external citation, the metamaterial can be reconfigured in real-time for desired behaviors.
		For example, a self-adaptive metasurface equipped with motion and light sensors have been developed in \cite{Ma2019} for single- and multi-beam steering.

		Next, we discuss the principles of electromagnetic wave redirection via refraction and reflection:
		\begin{itemize}
			\item \emph{Refraction:} As shown in Fig. \ref{fg:nim_focus}, the negative-index material can re-focus the beams diverging from a point source to another point behind the material \cite{Padilla2006}. This could be helpful for wireless applications where the transmitter and receiver are at different sides of the material.
			\item \emph{Reflection:} As shown in Fig. \ref{fg:wave_reflected}, the scattering elements cooperatively alter the phase of the incident wave for a constructive (or destructive) superposition of the reflected waves in the target direction \cite{Poulakis2022}. This could be helpful for wireless applications where the transmitter and receiver are at the same side of the material.
		\end{itemize}
		% electromagnetic wave refraction and reflection.

		\begin{figure}[H]
			\centering
			\subfloat[Negative-index material\label{fg:nim_focus}]{
				\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_focus.tex}
				}
			}
			\subfloat[Positive-index material\label{fg:pim_diverge}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/chapter_2/pim_diverge.tex}
				}
			}
			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point.}
		\end{figure}
		\begin{figure}[H]
			\centering
			\subfloat[Incident wave\label{fg:wave_incident}]{
				\resizebox{!}{4.04cm}{
					\input{assets/chapter_2/wave_incident.tex}
				}
			}
			\subfloat[Reflected wave\label{fg:wave_reflected}]{
				\resizebox{!}{4cm}{
					\input{assets/chapter_2/wave_reflected.tex}
				}
			}
			\caption{Reflection through metamaterials. Yellow dots represent scattering elements. Solid and dashed lines denote wavefronts and rays, respectively. The scattering elements work together to manipulate the phases of incident waves, resulting in a focused beam steered in the intended direction.}
		\end{figure}
		It is worth noticing that refraction and reflection are different implementations of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
		In the next subsection, we will some typical \gls{ris} scattering models and their physical architecture.
	\end{subsection}

	\begin{subsection}{Wave Scattering Models}
		\begin{subsubsection}{Principles}\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into and collect from the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			It is worth mentioning that
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or simply regarded a \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient that can be altered by load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2022a}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			More accurate models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and measurement fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsubsection}

@@

		\begin{subsubsection}{\glsfmtfull{bd} Model}
			How to model the \gls{ris} response if the passive scattering elements can be cooperative instead of independent?
			This question has been answered by \cite{Shen2020a} where a \gls{bd} model was proposed.
			From a network theory perspective \cite{Ivrlac2010}, the interaction between the scattering elements can be modelled as lossless (but not necessarily symmetric) in-group connections in an $N_\mathrm{S}$-port circuit network, as shown in Figs. \ref{fg:bd_ris_architecture_1} and \ref{fg:bd_ris_architecture_2} \cite{Shen2020a}.
			This architecture allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group.
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
				}
				\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: Modified from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_1}
			\end{figure}
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_2.eps}
				}
				\caption{Network model of an 8-element \gls{ris} with group-wise cooperative scattering of group size (a) 2 and (b) 4. The group size is a design parameter to balance the circuit complexity and scattering performance. Source: Modified from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_2}
			\end{figure}

			A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
			With symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
			\begin{equation}
				\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I}),
			\end{equation}
			which satisfies both \emph{symmetric} and \emph{unitary} properties
			\begin{subequations}
				\begin{equation}
					\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T},
					\label{eq:symmetric_property}
				\end{equation}
				\begin{equation}
					\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}.
					\label{eq:unitary_property}
				\end{equation}
			\end{subequations}
			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} such that the symmetric constraint \eqref{eq:symmetric_property} can be relaxed.
			This corresponds to the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as widely considered in quantum physics.
			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary blocks}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) =
				\begin{bmatrix}
					\mathbf{\Theta}_1 & \mathbf{0} & \cdots & \mathbf{0} \\
					\mathbf{0} & \mathbf{\Theta}_2 & \cdots & \mathbf{0} \\
					\vdots & \vdots & \ddots & \vdots \\
					\mathbf{0} & \mathbf{0} & \cdots & \mathbf{\Theta}_G
				\end{bmatrix},
				\label{eq:bd_scattering_matrix}
			\end{equation}
			where \eqref{eq:unitary_property} is equivalently denoted as $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
			The group size $L$ is a design parameter to balance the circuit complexity and scattering performance.
			Diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be viewed as extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
			Therefore, the \gls{bd} model \eqref{eq:bd_scattering_matrix} is envisioned to be the next-generation theoretical foundation for passive \gls{ris}, which grants more design freedom and stronger signal processing capability.

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2024}.
			One element is in the same group with another if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsubsection}
	\end{subsection}
\end{section}

@@

		Radiative \gls{wpt}\footnote{In the following part of the thesis, \gls{wpt} refers to radiative \gls{wpt}.} brings numerous opportunities to future wireless networks.
		First, it completely eliminates wired connections and can be integrated into existing wireless systems with minimum modifications.
		Those properties translate to simple deployment, high scalability, and low maintenance cost.
		Second, the power can be simultaneously radiated to multiple devices on demand in a predictable, sustainable and reliable manner.
		This supports our initial vision and is different from other uncontrollable and intermittent energy sources.
		Third and most importantly, radio waves carries power and information simultaneously.
		\gls{wpt} can therefore be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
		However, energy efficiency and safety concerns have been two major obstacles that limit the practical development of \gls{wpt}.
		In Section \ref{sc:swipt}, we will discuss how \gls{ris} can help address these issues.
	\end{subsection}

@@

		The block diagram a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
		The \gls{rf} signal is generated and radiated by the energy transmitter, propagated through a wireless channel in the presence of a \gls{ris}, captured by the antenna(s) at the receiver, converted to \gls{dc} power by rectifier(s), then passed to the power management unit.
		Upon successful harvesting, the \gls{dc} power is either delivered directly to the device or stored in a battery/super capacitor for future operations.
		When a feedback link is available, one can acquire \gls{csi} at the energy transmitter and exploit it for signal optimization.
		Such a closed-loop \gls{ris}-aided \gls{wpt} system can provide a complete control of transmitter, channel, and receiver, which is essential for maximizing the end-to-end power transfer efficiency
		\begin{equation}
			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4},
		\end{equation}
		where $P_{\mathrm{DC}}^\mathrm{T}$ is the transmitted \gls{dc} power, $P_{\mathrm{RF}}^\mathrm{T}$ is the transmitted \gls{rf} power, $P_{\mathrm{RF}}^\mathrm{R}$ is the received \gls{rf} power, $P_{\mathrm{DC}}^\mathrm{R}$ is the received \gls{dc} power, and $P_{\mathrm{DC}}^\mathrm{S}$ is the stored \gls{dc} power.
		The power conversion efficiencies are specified below:
		\begin{itemize}
			\item $\eta_1$: Transmitter \gls{dc}-to-\gls{rf} conversion efficiency\footnote{This is different from \gls{pae} used in amplifier rating, which takes into account both \gls{dc} power and input waveform power \cite{Joung2015}.} that depends on the \gls{rf} power amplifier and transmit antenna. It is also called ``drain efficiency'' and state-of-the-art designs can achieve $\eta_1 \ge 70\%$ \cite{Alizadeh2020}.
			\item $\eta_2$: Channel \gls{rf}-to-\gls{rf} conversion efficiency that depends on the wireless environment and \gls{ris} configuration. This is the major bottleneck of \gls{wpt} since the radiated power is inversely proportional to the propagation distance squared.
			\item $\eta_3$: Receiver \gls{rf}-to-\gls{dc} conversion efficiency that depends on the impedance matching and rectifier design. We will discuss its behavior and modelling in the next subsection.
			\item $\eta_4$: Storage \gls{dc}-to-\gls{dc} conversion efficiency that depends on the converter circuit and battery characteristics. Modern power management units can achieve a charging efficiency $\eta_4 \ge 90\%$ \cite{Tan2012}.
		\end{itemize}
		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the characteristics of input waveform like power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
		Extensive efforts have been contributed from \gls{rf}, wireless communications, and power electronic communities to improve the conversion efficiency of individual modules.
		However, it is often overlooked in the literature that a practical \gls{wpt} system is highly \emph{non-linear} since the amplifier and rectifier are very sensitive to the input waveform.
		This non-linear behavior can lead to a \emph{coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
		Besides, the system modeling and analysis are subject to practical constraints like diode threshold and reverse-breakdown voltages, device parasitics, impedance mismatch, and harmonic generation  \citep{Valenta2014}.
	\end{subsection}

	\begin{subsection}{Non-Linear Harvester Behavior}
		\begin{subsubsection}{Equivalent Circuits}
			\begin{figure}[H]
				\centering
				\subfloat[Rectenna]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/rectenna.tex}
					}
					\label{fg:rectenna}
				}
				\subfloat[Half-wave rectifier]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/halfwave_rectifier.tex}
					}
					\label{fg:halfwave_rectifier}
				}
				\caption{
					Equivalent circuit of (a) rectenna and (b) single-diode half-wave rectifier.
				}
				\label{fg:harvester_circuit}
			\end{figure}
			The rectifier is a nonlinear circuit that converts the \gls{rf} signal to \gls{dc} power by rectifying and filtering the input signal.
			Figs. \ref{fg:harvester_circuit} illustrates the equivalent circuits of a rectenna (antenna and rectifier) and a single-diode half-wave rectifier, where $v_{\mathrm{S}}$ is the source voltage on the receive antenna, $Z_{\mathrm{A}} = R_{\mathrm{A}} + \jmath X_{\mathrm{A}}$ is the antenna impedance, $Z_{\mathrm{in}} = R_{\mathrm{in}} + \jmath X_{\mathrm{in}}$ is the total impedance of the matching network and rectifier, $v_{\mathrm{in}}$ is input voltage on the matching network and rectifier, $v_{\mathrm{D}}$ is the diode voltage, $C$ is the buffer capacitance, $R_{\mathrm{L}}$ is the rectifier load resistance, and $v_{\mathrm{out}}$ is the output voltage.
			It is worth mentioning that the half-wave rectifier is the most popular choice in \gls{wpt} literature due to its simple behavior and low cost.
			Other rectifier topologies like full-wave, bridge, and voltage doubler can potentially improve the \gls{rf}-to-\gls{dc} conversion efficiency \cite{Rotenberg2020}, but their modeling and analysis are much more complicated.
		\end{subsubsection}

@@

			Generally speaking, the behavior of any rectenna can be separated into three operation regions \cite{Clerckx2016a}:

>>>>

		Conventional metamaterials have fixed properties that depend on the geometry and arrangement of their constituent elements.
		Once fabricated, these properties cannot be easily changed unless the structure is physically altered.
		This limits their early usage to military, with applications such as invisibility cloaks and optical illusions.
		In 2014, the concept of ``coding'' and ``programmable'' metamaterials was validated by researchers at Southeast University \cite{Cui2014}, who realized digital control of radar cross-section using biased diodes and \gls{fpga}.
		With a proper model of the target properties and external citation, the metamaterial can be reconfigured in real-time for desired behaviors.
		For example, a self-adaptive metasurface equipped with motion and light sensors have been developed in \cite{Ma2019} for single- and multi-beam steering.

		Next, we discuss the principles of electromagnetic wave redirection via refraction and reflection:
		\begin{itemize}
			\item \emph{Refraction:} As shown in Fig. \subref*{fg:nim_focus}, the negative-index material can re-focus the beams diverging from a point source to another point behind the material \cite{Padilla2006}. This could be helpful for wireless applications where the transmitter and receiver are at different sides of the obstacle.
			\item \emph{Reflection:} As shown in Fig. \subref*{fg:wave_reflected}, the scattering elements cooperatively alter the phase of the incident wave for a constructive (or destructive) superposition of the reflected waves in the target direction \cite{Poulakis2022}. This could be helpful to concentrate ambient electromagnetic energy within a specific area.
		\end{itemize}
		% electromagnetic wave refraction and reflection.

		\begin{figure}[H]
			\centering
			\subfloat[Negative-index material\label{fg:nim_focus}]{
				\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_focus.tex}
				}
			}
			\subfloat[Positive-index material\label{fg:pim_diverge}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/chapter_2/pim_diverge.tex}
				}
			}
			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point behind the material.}
		\end{figure}
		\begin{figure}[H]
			\centering
			\subfloat[Incident wave\label{fg:wave_incident}]{
				\resizebox{!}{4.04cm}{
					\input{assets/chapter_2/wave_incident.tex}
				}
			}
			\subfloat[Reflected wave\label{fg:wave_reflected}]{
				\resizebox{!}{4cm}{
					\input{assets/chapter_2/wave_reflected.tex}
				}
			}
			\caption{Reflection through metamaterials. Yellow dots represent scattering elements. Solid and dashed lines denote wavefronts and rays, respectively. The scattering elements work together to manipulate the phases of incident waves, resulting in a focused beam steered in the intended direction.}
		\end{figure}
		It is worth noticing that refraction and reflection are different implementations of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
		In the next subsection, we will some typical \gls{ris} scattering models and their physical architecture.
	\end{subsection}

	\begin{subsection}{Wave Scattering Models}
		\begin{subsubsection}{Principles}\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			Specifically,
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or a baseband \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient and load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2024}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			Advanced models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and parametric fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature for accurate and practical analysis.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsubsection}

@@

		\begin{subsubsection}{\glsfmtfull{bd} Model}
			How to model the \gls{ris} response if the passive scattering elements can cooperate with neighbors via physical connections?
			This question has been answered by \cite{Shen2020a} through a \gls{bd} model.
			From a network theory perspective \cite{Ivrlac2010}, a general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
			It allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group, such that both amplitude and phase of the scattered wave can be redistributed with zero power loss.
			Fig. \ref{fg:bd_ris_architecture_2} illustrates an 8-element \gls{ris} with group size 2 (left) and 4 (right).
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_2.eps}
				}
				\caption{Network model of an 8-element \gls{ris} with group-wise cooperative scattering of group size (a) 2 and (b) 4. The group size is a design parameter to balance the circuit complexity and scattering performance. Source: Modified from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_2}
			\end{figure}

			% thus redistribute both amplitude and phase of the scattered wave with zero power loss.
			% \begin{figure}[H]
			% 	\centering
			% 	\resizebox{0.75\columnwidth}{!}{
			% 		\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
			% 	}
			% 	\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: Modified from \cite{Shen2020a}.}
			% 	\label{fg:bd_ris_architecture_1}
			% \end{figure}

			% A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
			With symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
			\begin{equation}
				\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I}),
			\end{equation}
			which satisfies both \emph{symmetric} and \emph{unitary} properties
			\begin{subequations}
				\begin{equation}
					\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T},
					\label{eq:symmetric_property}
				\end{equation}
				\begin{equation}
					\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}.
					\label{eq:unitary_property}
				\end{equation}
			\end{subequations}
			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} such that the symmetric constraint \eqref{eq:symmetric_property} is unnecessary.
			This corresponds to the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as has been widely adopted in quantum physics.
			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary diagonal blocks}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) =
				\begin{bmatrix}
					\mathbf{\Theta}_1 & \mathbf{0} & \cdots & \mathbf{0} \\
					\mathbf{0} & \mathbf{\Theta}_2 & \cdots & \mathbf{0} \\
					\vdots & \vdots & \ddots & \vdots \\
					\mathbf{0} & \mathbf{0} & \cdots & \mathbf{\Theta}_G
				\end{bmatrix},
				\label{eq:bd_scattering_matrix}
			\end{equation}
			where \eqref{eq:unitary_property} is equivalently denoted as $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
			The group size $L$ is a design parameter to balance the circuit complexity and scattering performance.
			Diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be viewed as extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
			Therefore, the \gls{bd} model \eqref{eq:bd_scattering_matrix} is envisioned to be the next-generation theoretical foundation for passive \gls{ris}, which grants more design freedom and stronger signal processing capability.

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2024}.
			Two elements are in the same group if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsubsection}
	\end{subsection}
\end{section}

@@

		Radiative \gls{wpt}\footnote{In the following part of the thesis, \gls{wpt} refers to radiative \gls{wpt}.} brings numerous opportunities to future wireless networks.
		First, it completely eliminates wired connections and can be integrated into existing wireless systems with minimum modifications.
		Those properties translate to simple deployment, high scalability, and low maintenance cost.
		Second, the power can be simultaneously radiated to multiple devices on demand in a predictable, sustainable and reliable manner.
		This fits in our initial vision and differs from other unstable energy sources.
		Third and most importantly, radio waves carries power and information simultaneously.
		\gls{wpt} can therefore be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
		However, energy efficiency and safety concerns have been two major obstacles that limit the practical development of \gls{wpt}.
		In Section \ref{sc:swipt}, we will discuss how \gls{ris} can help address these issues.
	\end{subsection}

@@

		The block diagram a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
		The \gls{rf} signal is generated and radiated by the energy transmitter, propagated through a wireless channel in the presence of a \gls{ris}, captured by the antenna(s) at the receiver, converted to \gls{dc} power by rectifier(s), then passed to the power management unit.
		Upon successful harvesting, the \gls{dc} power is either delivered directly to the device or stored in a battery/super capacitor for future operations.
		When a feedback link is available, one can acquire \gls{csi} at the energy transmitter and exploit it for signal optimization.
		Such a closed-loop \gls{ris}-aided \gls{wpt} system can provide a complete control of transmitter, channel, and receiver, which is essential for maximizing the end-to-end power transfer efficiency
		\begin{equation}
			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4},
		\end{equation}
		where $P_{\mathrm{DC}}^\mathrm{T}$ is the transmitted \gls{dc} power, $P_{\mathrm{RF}}^\mathrm{T}$ is the transmitted \gls{rf} power, $P_{\mathrm{RF}}^\mathrm{R}$ is the received \gls{rf} power, $P_{\mathrm{DC}}^\mathrm{R}$ is the received \gls{dc} power, and $P_{\mathrm{DC}}^\mathrm{S}$ is the stored \gls{dc} power.
		The power conversion efficiencies are specified below:
		\begin{itemize}
			\item $\eta_1$: Transmitter \gls{dc}-to-\gls{rf} conversion efficiency\footnote{This is different from \gls{pae} used in amplifier rating, which takes into account both \gls{dc} power and input waveform power \cite{Joung2015}.} that depends on the \gls{rf} power amplifier and transmit antenna. It is also called ``drain efficiency'' and state-of-the-art designs can achieve $\eta_1 \ge 70\%$ \cite{Alizadeh2020}.
			\item $\eta_2$: Channel \gls{rf}-to-\gls{rf} conversion efficiency that depends on the wireless environment and \gls{ris} configuration. This is the major bottleneck of \gls{wpt} since the radiated power is inversely proportional to the propagation distance squared.
			\item $\eta_3$: Receiver \gls{rf}-to-\gls{dc} conversion efficiency that depends on the impedance matching and rectifier design. We will discuss its behavior and modelling in the next subsection.
			\item $\eta_4$: Storage \gls{dc}-to-\gls{dc} conversion efficiency that depends on the converter circuit and battery characteristics. Modern power management units can achieve a charging efficiency $\eta_4 \ge 90\%$ \cite{Tan2012}.
		\end{itemize}
		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the signal characteristics such as power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
		Extensive efforts have been contributed from \gls{rf}, wireless communications, and power electronic communities to improve the conversion efficiency of individual modules.
		However, it is often overlooked in the literature that a practical \gls{wpt} system is highly \emph{non-linear} since the amplifier and rectifier are very sensitive to the input waveform.
		This non-linear behavior can lead to a {coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
		Besides, the system modeling and analysis are subject to practical constraints like diode threshold and reverse-breakdown voltages, device parasitics, impedance mismatch, and harmonic generation  \citep{Valenta2014}.
	\end{subsection}

	\begin{subsection}{Non-Linear Harvester Behavior}
		\begin{subsubsection}{Equivalent Circuits}
			\begin{figure}[H]
				\centering
				\subfloat[Rectenna]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/rectenna.tex}
					}
					\label{fg:rectenna}
				}
				\subfloat[Half-wave rectifier]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/halfwave_rectifier.tex}
					}
					\label{fg:halfwave_rectifier}
				}
				\caption{
					Equivalent circuit of (a) rectenna and (b) single-diode half-wave rectifier.
				}
				\label{fg:harvester_circuit}
			\end{figure}
			The rectifier is a nonlinear circuit that converts the \gls{rf} signal to \gls{dc} power by rectifying and filtering the input signal.
			Fig. \ref{fg:harvester_circuit} illustrates the equivalent circuits of a rectenna (antenna and rectifier) and a single-diode half-wave rectifier, where $v_{\mathrm{S}}$ is the source voltage on the receive antenna, $Z_{\mathrm{A}} = R_{\mathrm{A}} + \jmath X_{\mathrm{A}}$ is the antenna impedance, $Z_{\mathrm{in}} = R_{\mathrm{in}} + \jmath X_{\mathrm{in}}$ is the total impedance of the matching network and rectifier, $v_{\mathrm{in}}$ is input voltage on the matching network and rectifier, $v_{\mathrm{D}}$ is the diode voltage, $C$ is the buffer capacitance, $R_{\mathrm{L}}$ is the rectifier load resistance, and $v_{\mathrm{out}}$ is the output voltage.
			It is worth mentioning that the half-wave rectifier is the most popular choice in \gls{wpt} literature due to its simple layout and low cost.
			Other rectifier topologies like full-wave, bridge, and voltage doubler can potentially improve the \gls{rf}-to-\gls{dc} conversion efficiency \cite{Rotenberg2020}, but their modeling and analysis are much more complicated.
		\end{subsubsection}

@@

			Roughly speaking, the behavior of any rectenna can be separated into three operation regions \cite{Clerckx2016a}:
